Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-28 numerical-starformation.tex
Minor star formation tweak.
ok, one more tweak.

\red{(BWO: can this whole paragraph go?)}
While the physics discussed in other sections of this paper is crucial
to the study of cosmological structure formation, most observations of
galaxies in the infrared, optical, and ultraviolet wavelengths are of
stellar populations.  Furthermore, stars eject energy and metal-
enriched gas throughout their lives, drastically modifying their own
environments' cooling properties.  Broadly speaking, the formation of
galaxies and galaxy clusters cannot be completely modeled without
including the feedback of energy and metals from stellar populations.
In particular, it is thought that feedback is crucial for suppressing
the large numbers of dwarf-like galaxies that CDM theories predict
\citep{1991ApJ...381...14L,1991ApJ...379...52W}.  An early burst of
star formation could remove a large fraction of cold gas from such
systems \citep{1978MNRAS.183..341W,1991ApJ...367...45C}.  Also, the
unexpectedly low luminosities of small clusters and groups (relative
to the richest clusters) is commonly explained through feedback
\citep{1991ApJ...383..104K}.  Energy ejected during the formation of
the cluster ellipticals lowers the central density and hence the X-ray
luminosity of such clusters \citep{1997ApJ...484L..21C}.  For all of
these reasons, it is critical to include star formation and the
feedback of energy and metals into the interstellar and intergalactic
media in cosmological simulations.

@@

Feedback from Population III stars created using this algorithm comes in multiple forms.
Radiative feedback using the \moray\ radiation transport algorithm
\citep{Wise11_Moray} is available, using the mass-dependent hydrogen
ionizing and Lyman-Werner photon luminosities and lifetimes of the
Population III stars from \citet{2002A&A...382...28S}.  At the end of
their main-sequence lifetimes, explosion energies, ejected gas mass,
and ejected metal are caclulated using a variety of sources that
depend on the mass of the star, and are described in detail in Section
3.2.1 of \citet{2012MNRAS.427..311W}.

>>>>

% \red{(BWO: can this whole paragraph go?)}
% While the physics discussed in other sections of this paper is crucial
% to the study of cosmological structure formation, most observations of
% galaxies in the infrared, optical, and ultraviolet wavelengths are of
% stellar populations.  Furthermore, stars eject energy and metal-
% enriched gas throughout their lives, drastically modifying their own
% environments' cooling properties.  Broadly speaking, the formation of
% galaxies and galaxy clusters cannot be completely modeled without
% including the feedback of energy and metals from stellar populations.
% In particular, it is thought that feedback is crucial for suppressing
% the large numbers of dwarf-like galaxies that CDM theories predict
% \citep{1991ApJ...381...14L,1991ApJ...379...52W}.  An early burst of
% star formation could remove a large fraction of cold gas from such
% systems \citep{1978MNRAS.183..341W,1991ApJ...367...45C}.  Also, the
% unexpectedly low luminosities of small clusters and groups (relative
% to the richest clusters) is commonly explained through feedback
% \citep{1991ApJ...383..104K}.  Energy ejected during the formation of
% the cluster ellipticals lowers the central density and hence the X-ray
% luminosity of such clusters \citep{1997ApJ...484L..21C}.  For all of
% these reasons, it is critical to include star formation and the
% feedback of energy and metals into the interstellar and intergalactic
% media in cosmological simulations.

@@

Feedback from Population III stars created using this algorithm comes in multiple forms.
Radiative feedback using the Moray radiation transport algorithm
\citep{Wise11_Moray} is available, using the mass-dependent hydrogen
ionizing and Lyman-Werner photon luminosities and lifetimes of the
Population III stars from \citet{2002A&A...382...28S}.  At the end of
their main-sequence lifetimes, explosion energies, ejected gas mass,
and ejected metal are caclulated using a variety of sources that
depend on the mass of the star, and are described in detail in Section
3.2.1 of \citet{2012MNRAS.427..311W}.
